\documentclass[10pt,a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}

% Layout and styling.
\usepackage[margin=1.5cm]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{microtype}

% Spacing.
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.1em}
\setlist[itemize]{itemsep=0.08em,topsep=0.08em,left=1.2em}

% Section styling.
\newcommand{\sectionseparator}{\vspace{-0.5em}\noindent\color{black!20}\rule{\linewidth}{0.5pt}\vspace{0.1em}}
\titleformat{\section}{\large\bfseries}{}{0pt}{}[\sectionseparator]
\titlespacing*{\section}{0pt}{0.4em}{0.1em}

% Entry layout macro.
\newcommand{\entry}[3]{\noindent\textbf{#1} — #2\hfill #3\\}

% Tech stack macro for projects
\newcommand{\techstack}[1]{\textcolor{black!70}{\small\textit{#1}}}

% Personal details.
\newcommand{\Name}{Karolis Strazdas}
\newcommand{\Email}{karolis.strazdas@protonmail.com}
\newcommand{\Website}{https://karolis-strazdas.lt}
\newcommand{\GitHub}{https://github.com/Eoic}
\newcommand{\LinkedIn}{https://www.linkedin.com/in/karolis-strazdas/}

\begin{document}

\pagestyle{empty}

\begin{center}
{\Huge\bfseries \Name}\\[0.8em]
\small \href{mailto:\Email}{\Email} \quad\textbullet\quad \href{\Website}{karolis-strazdas.lt} \quad\textbullet\quad \href{\GitHub}{github.com/Eoic} \quad\textbullet\quad \href{\LinkedIn}{linkedin.com/in/karolis-strazdas}
\end{center}

\vspace{-0.65em}

% Use a slightly smaller body font to keep the CV compact.
\begingroup\small

\section*{Profile}
Software engineer with 5+ years of experience building full-stack applications. I enjoy working on challenging problems, shipping reliable software, and automating workflows favoring efficient and maintainable solutions.

\section*{Experience}
\entry{Indeform Ltd.}{Software Engineer}{2020-07 -- Present}
\vspace{-0.8em}
\begin{itemize}[leftmargin=*,itemsep=0.0em,topsep=0.02em]
  \item Delivered order management and 3D mesh editing features (polyline slicing, deformations) for an orthopedic modeling platform (Django, MySQL, Three.js); ported Rhino scripts to WebGL, enabling precise mesh modifications on orthopedic models.
  \item Built ML pipelines for wear prediction and defect detection on multivariate time series (piezoelectric, force, vibration, AE, displacement); authored literature review, project reports, and packaged models for testing in real-world conditions; F1~\textasciitilde0.94, MAE~\textasciitilde0.09\,mm, $R^2$~\textasciitilde0.96.
  \item Shipped a company\mbox{-}wide internal web platform for project and team management, onboarding and communications with a custom role\mbox{-}based access system.
  \item Set up CI/CD and infrastructure (Docker, Nginx, Jenkins) for deployments on AWS EC2 and on\mbox{-}premises, with load balancing and minimal downtime.
  \item Built multiple interactive projection installations with OpenCV, C++, Python, Godot, and ImGui; deployed to a museum; implemented robust ball tracking system and parallelized camera frame buffering for reliable real-time input handling.
  \item Authored TestLink scenarios and added Cypress integration tests for critical workflows, improving pre\mbox{-}release defect discovery.
\end{itemize}

\vspace{0.2em}

\entry{Indeform Ltd.}{Software Engineer Intern}{2020-02 -- 2020-05}
\vspace{-0.8em}
\begin{itemize}[leftmargin=*,itemsep=0.0em,topsep=0.02em]
  \item Participated in requirements and domain modeling sessions; helped define scope, workflows, and success criteria.
  \item Delivered an MVP debt recovery web app (case intake, repayment plans, tiered email reminders, reporting).
  \item Designed database schema and web APIs; implemented document and CSV uploading, processing and management.
  \item Built with Django and PostgreSQL, added unit and integration tests, deployed behind Apache.
\end{itemize}

\section*{Education}
\entry{Kaunas University of Technology}{Bachelor of Software Engineering}{2016 -- 2020}
\entry{Kaunas University of Technology}{Master of Artificial Intelligence in Computer Science}{2025 -- 2027 (exp.)}
\vspace{-0.8em}

\section*{Skills}
\textbf{Programming:} Python, JavaScript/TypeScript, Elixir, Rust.\\
\textbf{ML/Data:} scikit-learn, TensorFlow, OpenCV.\\
\textbf{DevOps/Infrastructure:} Docker, Docker Compose, Nginx, Apache, Jenkins, AWS.\\
\textbf{Tools/Other:} Godot, ImGui, Django, Three.js.

\section*{Personal projects}
\begin{itemize}[leftmargin=*,itemsep=0.08em,topsep=0.08em]
  \item \textbf{TimeLab} -- Local-first time series data labeling tool.\\
      \techstack{TypeScript, SCSS} | \url{https://github.com/Eoic/TimeLab}
  \item \textbf{Papyrus} -- Cross-platform e-book management system.\\
      \techstack{Python, Dart, Flutter, FastAPI, PostgreSQL} | \url{https://github.com/Eoic/Papyrus}
  \item \textbf{ASCIIGround} -- TypeScript library for animated character backgrounds.\\
      \techstack{TypeScript} | \url{https://github.com/Eoic/ASCIIGround}
  \item \textbf{NetBots} -- Real-time multiplayer robot programming game.\\
      \techstack{TypeScript, Python, Rust, MongoDB, Pixi.js} | \url{https://github.com/Eoic/NetBots}
  \item \textbf{Canopy} -- Real-time spatial conversation platform.\\
      \techstack{Python, TypeScript, Pixi.js} | \url{https://github.com/Eoic/Canopy}
  \item More projects: \url{https://karolis-strazdas.lt}
\end{itemize}

\section*{Languages}
Lithuanian — Native \;\;|\;\; English — Professional working proficiency

\section*{Interests}
Reading, cycling, running, personal programming projects, and learning new things in tech and science.

\endgroup
\end{document}
